Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-29 ltx/data_paper/DataPaper.tex
edit to correlation analysis

From \eqref{eq:EM-Fourier_TF_of_Kernel} it can be observed that an error in our guess for $\xi$ will result in a dilation or contraction of the estimated kernel support and an incorrect estimate in the observation noise will result in a distortion in the shape of the kernel, however if the signal to noise ratio is high such a distortion would be insignificant. The denominator in equation \eqref{eq:EM-Fourier_TF_of_Kernel} is in fact the power spectral density of noise free observations which is non-negative and real. This important result is known as Weiner-Khintchine (W-K) theorem in signal processsing which states that the power spectral density of the wide sense stationary process is the Fourier transform of its autocorrelation function \cite{Ricker2003}. The numerator is also called the cross spectrum or cross spectral density. Since the connectivity kernel is a real function, the following relation holds \cite{Bracewell2000}

>>>>

From \eqref{eq:EM-Fourier_TF_of_Kernel} it can be observed that an error in our guess for $\xi$ will result in a dilation or contraction of the estimated kernel support and an incorrect guess of the observation noise will result in a distortion in the shape of the kernel, however if the signal to noise ratio is high such a distortion becomes insignificant. The denominator in \eqref{eq:EM-Fourier_TF_of_Kernel} is in fact the power spectral density of the noise-free observations and is a non-negative and real quantity. This  is known as Weiner-Khintchine (W-K) theorem in signal processing which states that the power spectral density of the wide sense stationary process is the Fourier transform of its autocorrelation function \cite{Ricker2003}. The numerator is also known as the cross-spectrum or cross-spectral density. Since the connectivity kernel is a real function, the following relation holds \cite{Bracewell2000}
